Refinements for open automata

### 2022-12-15 2021-Refinement/paper/refinementarticleV2.tex
reformulation

\begin{definition}[Hole-equal simulation]
Consider two OA with identical set of holes:  \(\OAg[1]\) and \(\OAg[2]\) where  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold: 
\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
\noindent\begin{multline*}
 \bigsymb{\forall} {t_1} = \openrule
         {
           \beta_{1 j}^{j\in J}, g_1,\psi_1}
         {s_1 \OTarrow {\alpha_1} s_1'} \in \fOT{s_1} .\,~~
\bigsymb{\bigexists} 
\mpar{t_{2x} \!=\! \openrule
         {
           \beta_{2 x j}^{j\in J}, g_{2 x},\psi_{2 x}}
         {s_2 \OTarrow {\alpha_{2 x}} s_{2 x}'}
}^{x \in X}\in \fOT{s_2}.\,~~\\ 
\everymath{\displaystyle}\begin{array}{l}
V_1 \uplus V_2 \uplus  \fvars{t_1} \uplus \bigcup_x\fvars{t_{2x}}  \vdash
\\
 R\mpar{s_1, s_2} \wedge g_1 \implies
 \operatorname*{\bigsymb{\bigvee}}_{x \in X}
\mpar{\begin{array}{l}
			\alpha_{2x} = \alpha_{1} \wedge \bigwedge_\subbox{j \in J} \beta_{2xj} = \beta_{1j} \nwedge\\[12pt]
			 g_{2x} \wedge R\mpar{ s'_{1},s'_{2x}}\psubst{\psi_{2x} \uplus \psi_{1}}
		\end{array}} 
\end{array} 
\end{multline*}
\item [(3)] The deadlock reduction:
\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \wedge \lnot( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
\end{multline*}

>>>>

\begin{definition}[Hole-equal simulation]
Consider two OA with identical set of holes:  \(\OAg[1]\) and \(\OAg[2]\) where  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold (we could denote it $T_1\leq T_2$): 
\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
\noindent\begin{multline*}
 \bigsymb{\forall} {t_1} = \openrule
         {
           \beta_{1 j}^{j\in J}, g_1,\psi_1}
         {s_1 \OTarrow {\alpha_1} s_1'} \in \fOT{s_1} .\,~~
\bigsymb{\bigexists} 
\mpar{t_{2x} \!=\! \openrule
         {
           \beta_{2 x j}^{j\in J}, g_{2 x},\psi_{2 x}}
         {s_2 \OTarrow {\alpha_{2 x}} s_{2 x}'}
}^{x \in X}\in \fOT{s_2}.\,~~\\ 
\everymath{\displaystyle}\begin{array}{l}
V_1 \uplus V_2 \uplus  \fvars{t_1} \uplus \bigcup_x\fvars{t_{2x}}  \vdash
\\
 R\mpar{s_1, s_2} \wedge g_1 \implies
 \operatorname*{\bigsymb{\bigvee}}_{x \in X}
\mpar{\begin{array}{l}
			\alpha_{2x} = \alpha_{1} \wedge \bigwedge_\subbox{j \in J} \beta_{2xj} = \beta_{1j} \nwedge\\[12pt]
			 g_{2x} \wedge R\mpar{ s'_{1},s'_{2x}}\psubst{\psi_{2x} \uplus \psi_{1}}
		\end{array}} 
\end{array} 
\end{multline*}
\item [(3)] The deadlock reduction:
\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \wedge \lnot( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
\end{multline*}

Which can be rewritten as:
\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
\end{multline*}
